Pytorch-Bert-Text-Infilling

### 2020-10-26 scripts/model_starters/R/Pytorch-Bert-Text-Infilling.Rmd
update Pytorch-Bert-Text-Infilling

>>>>

## Updated prediction unction

```{r, warning=FALSE}
##### Prediction function
predict_tokens <- function(text_original) {
  ### Clean text
  text_stripped <- strip(text_original, char.keep = c("?", ".", "’", "~~"), digit.remove = TRUE, apostrophe.remove = FALSE,
                         lower.case = FALSE)
  ### Collect text errors
  errors <- hunspell(text_stripped)

  ### Replace errors to [MASK]
  for(e in errors){
    pats <- paste(e, collapse = '|')
  }
  text <- str_replace_all(text_stripped, pats, '[MASK]')

  ### Tokenize the text
  tokenized_text <- tokenizer$tokenize(text)
  indexed_tokens <- tokenizer$convert_tokens_to_ids(tokenized_text)

  ### Encode the text and create segments tensors
  MASKIDS <- which(tokenized_text == "[MASK]")
  SEGS <- which(tokenized_text == ".")

  segments_ids <- rep(as.integer(0), times = SEGS)

  segments_tensors <- torch$tensor(list(segments_ids))
  tokens_tensor <- torch$tensor(list(indexed_tokens))

  ### Generate prediction
  py <- torch$no_grad()
  with(py, {
    predictions <- model(tokens_tensor, segments_tensors)
  })

  predicted_token <- list()
  for(i in 1:length(MASKIDS)){
    preds <- torch$topk(predictions[[0]][MASKIDS[i]], k=as.integer(50))
    indices <- preds$indices$tolist()
    list <- tokenizer$convert_ids_to_tokens(indices)
    predicted_token <- append(predicted_token, list(list[1]))
  }
  predicted_token.i <- 1

predict_tokens(text_original)
```
